---
title             : "PREVIC: An Item Response Theory based parent report measure of expressive vocabulary in children between 3 and 8 years of age"
shorttitle        : "Parental report measure of vocabulary"

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Julia Prein"
    affiliation   : "2"
    role:
      - Conceptualization
      - Software
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      
  - name          : "Tobias Koch"
    affiliation   : "3"
    role:
      - Formal Analysis
      - Writing - Review & Editing
  
  - name          : "Maximilian Bee"
    affiliation   : "3"
    role:
      - Formal Analysis
      - Writing - Review & Editing
      
  - name          : "Daniel Haun"
    affiliation   : "2"
    role:
      - Conceptualization
      - Writing - Review & Editing
      
  - name          : "Natalia Gagarina"
    affiliation   : "4"
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Institute for Psychology, Leuphana University Lüneburg, Germany"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "3"
    institution   : "Institut of Psychology, Friedrich-Schiller-University Jena, Germany"
  - id            : "4"
    institution   : "Leibniz-Zentrum Allgemeine Sprachwissenschaft, Berlin, Germany"

authornote: |
  We thank Susanne Mauritz for her help with the data collection.

abstract: |
  lore ipsum.
  
keywords          : "language development, vocabulary, individual differences, Item Response Models"
wordcount         : "X"

bibliography      : "./library.bib"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(readxl)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

Learning language is one of the key developmental objectives for children. This learning process is highly variable and leads to persistent individual differences which are related to a wide range of outcome measures later in life [@bornstein2018stability; @schoon2010children; @morgan201524; @marchman2008speed; @walker1994prediction; @bleses2016early; @golinkoff2019language; @pace2017identifying; @pace2019measuring]. For example, in a longitudinal study spanning 29 years, @schoon2010children found that relatively poorer language skills at age five were associated with lower levels of mental health at age 34. Given their high predictive validity, high-quality measures are needed to assess early language abilities.

Child language measures can be broadly categorized into two types: direct and parent report measures. Direct measures are generally used with children of three years and older. Direct expressive language assessments involve prompting children to generate words or sentences in response to a given stimulus, such as a picture depicting a scene or an object. Direct receptive language assessments require children to match a verbal prompt with a corresponding picture of a scene or object. Various direct measures tailored to different languages and age groups have been developed, including measures for English and German [@dunn1965peabody; @dunn1997british; @golinkoff2017user; @kiese2005awst; @kauschke2002patholinguistische; @lenhard2015peabody; @gluck2011wortschatz]. Additionally, standardized cognitive ability tests frequently incorporate direct language measures [e.g., @bayley2006bayley; @wechsler1949wechsler; @gershon2013iv]. 

Parent report measures are widely utilized in psychological research. They are particularly popular as screening methods to identify developmental delays [@diamond1993role; @pontoppidan2017parent]. However, it is important to acknowledge that parent reports come with certain caveats, including the potential for selective reporting and social desirability bias. As a consequence, providing a comprehensive assessment of the overall quality and usefulness of these measures is challenging [@morsbach2006understanding]. Nonetheless, some parent report measures have been found to be both reliable and valid [@hornman2013validity; @ireton1995assessin; @macy2012evidence; @bodnarchuk2004can; @saudino1998validity].

In child language research, parent report measures are often utilized with very young children when direct assessment is challenging. One widely used measure is the MacArthur-Bates Communicative Development Inventories (CDI) [@fenson2007macarthur]. The CDI asks parents to to check those words from a checklist that they believe their child produces and/or understands. This measure has been adapted for a wide range spoken and signed languages [see @frank2021variability for an overview], with various versions available [e.g., @makransky2016item; @mayor2019short], including an online version [@demayo2021web]. Collaborative efforts have facilitated the pooling of data from thousands of children learning different languages into centralized repositories [@frank2017wordbank; @jorgensen2010clex]. Importantly, the CDI exhibits validity as parental reports align with direct observations and assessments of child language [@bornstein1998vocabulary; @fenson1994variability; @dale1991validity; @feldman2005concurrent].

However, the use of the CDI -- in typically developing children -- is limited to 37 months of age. Beyond this point, most children are reported to say all the words on the list. Consequently, there is a need for a comparable measure that can be applied to older children, as parental reports offer a convenient and comprehensive means of assessing children's language abilities and provide a complementary perspective on development. Existing instruments focusing on general cognitive development often include language scales; however, these scales lack detailed information and fail to capture individual differences effectively [@ireton1995assessin]. For example, the Ages and Stages Questionnaire (ASQ) at 36 months comprises only six items that encompass general communicative behavior, such as whether the child can say their full name when prompted [@squires2009ages]. One notable example of a dedicated language measure for older children is the Developmental Vocabulary Assessment for Parents [DVAP, @libertus2015developmental]. The DVAP is derived from the words used in the Peabody Picture Vocabulary Test [PPVT; @dunn1965peabody], a widely used direct measure of receptive vocabulary. As perhaps expected, the DVAP demonstrates high validity, as evidenced by its strong correlation with the PPVT. However, the proprietary nature of the PPVT limits the utility of the DVAP for researchers.^[When the first author approached the license holder of the PPVT in Germany to ask if we could use the words to build a parental report measure, we were told that we would have to pay for every administration of the new measure and we would not be allowed to openly share the materials.] As a consequence, it is unlikely that comparable "success story" -- as observed with the CDI -- will emerge where researchers have adapted the original English form to different languages and more efficient forms. 

More general issue with langueage measures is lack of psychometric considerations during development. The developmental process is not transparent IRT provides a toolkit that is very useful for development. Each item is assessed in its usefulness to measure a latent construct at different ages

# The current study

Our goals was to develop a high-quality and easy-access vocabulary checklist for children between three and eight years of age. The measure and all associated materials should be openly available for other researchers to use. To ensure the quality of the items, we created a large initial item pool from which we selected high-quality items. To ensure easy-access, we implemented the checklist as an interactive web-app.


# Task design an implementation 

# Item pool generation 

# Item selection

## Participants

## Descriptive results

## Automated item selection

## Differential item functioning

# Psychometric properties of new checklist

## Reliability

## Convergent validity

# Discussion 

Measure is likely different in type from CDI. Especially early in life, CDI likely captures the entire vocabulary.

## Limitations

Not a representative sample

## Conclusion


# Open Practices Statement 

The task can be accessed via the following website: https://ccp-odc.eva.mpg.de/orev-demo/. The corresponding source code can be found in the following repository: https://github.com/ccp-eva/orev-demo. The data sets generated during and/or analysed during the current study are available in the following repository: https://github.com/ccp-eva/orev/. Data collection was preregistered at: https://osf.io/qzstk.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
